\chapter{Evaluation}

\section{Customer Requirements}

Below is a list of all my general and specific objectives that I set myself in the analysis section. In this section I will determine whether I have met all of these objectives and the reasoning behind it. The subsections with *NEW* in the title are objectives that I did not identify in my analysis section; however during the course of my implementation, I attempted to meet the objectives. 

\subsection{Aesthetically pleasing, easy to navigate GUI.}

\subsection{Videos organised and filtering capabilities.}

\subsection{Correct and accurate mapping to the skate parks/spots.}

\subsection {Correct directions from current location to skate park/ spot on the map.}

\subsection{Non-biased reviews.}

\subsection{Clear database with a list of tricks in.}

\subsection{ Easy to filter through tricks known.}

\subsection {Display status bar messages at appropriate times to inform the user of changes *NEW*}

\subsection {Allow for the user to contact the developer *NEW*}

\subsection {Ensure that the profile picture can be changed easily *NEW*}

\subsection {Ensure that the profile name can be edited easily *NEW*}

\subsection {Ensure that the profile email can be edited easily *NEW*}


\subsection {Ensure that videos can be filtered by categories. e.g easy, medium, hard tricks.}

\subsection {Ensure that videos load correctly and are linked to the right video.}

\subsection {Ensure that videos are displayed at the correct size/resolution that the monitor of the computer is.}



\subsection {Ensure the database can add, edit and remove trick data (Name, description, image, completed status and tutorial link).}

\subsection {Ensure that the database is displayed correctly inside the application at all resolutions.}

\subsection {Ensure that the tricks are marked by how hard they are by a three way scale of: Easy, Medium or Hard.}

\subsection {Ensure a checkbox is by the side of a trick to represent whether the user has completed that trick or not.}

\subsection {Ensure there is a search bar for a specific trick name.}

\subsection {Ensure there are filters for tricks e.g Switch trick filters.}



\subsection {Ensure that the map is accurate to current roads.}

\subsection {Ensure location of the user is not revealed to anyone else.}

\subsection {Ensure that the current location marker is accurate.}

\subsection {Ensure that when giving directions to skate parks from your current location that the mapping route is correct and on viable roads. }

\subsection {Ensure that the program can mark skate park locations.}


\subsection {Ensure no biased reviews are posted to the app and that they're moderated before they are universally posted.}

\subsection {Ensure the program runs fast without lag when navigating between areas of the application.}



\section{Effectiveness}

%include as many subsections as necessary for your objectives - Only evaluate the objectives you met
\subsection{Objective Evaluation}

\section{Learnability}

\section{Usability}

\section{Maintainability}

\section{Suggestions for Improvement}

\section{End User Evidence}

\subsection{Questionnaires}

\subsection{Graphs}

\subsection{Written Statements}
